Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies

### 2018-07-13 main.tex
updates

%\documentclass[twocolumn]{aastex61}
%\pdfoutput=1 %for arXiv submission
\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{newtxtext,newtxmath}

%\usepackage{amsmath,amstext}
%\usepackage[T1]{fontenc}
\usepackage[figure,figure*]{hypcap}

\hypersetup{draft}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}

%\usepackage{apjfonts} 
%\usepackage{natbib} % bibliography

%\usepackage[active,floats,tightpage]{preview}
%    \setlength\PreviewBorder{1em}

%\shorttitle{Feedback with Individual Stars}
%\shortauthors{Emerick, Bryan, Mac Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

%%%%%%%%%%%%%%%%%%\hypersetup{draft}
% For bibtex

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

\author[A. Emerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

@@

\label{firstpage}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

%\author{Andrew Emerick}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\author{Greg L. Bryan}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
%\author{Mordecai-Mark Mac Low}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}

\begin{abstract}
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

\begin{keywords}
Galaxy -- Hydrodynamics -- Simulation -- Feedback
\end{keywords}

\section{Introduction}
%
% AE removed below.. MM suggested  skipping both pars.
%
%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics. 
%
%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. \textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. We describe each mode of our multi-channel feedback 
in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.

Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.

\section{Methods}
\label{sec:methods}
We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}). We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI. In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

\subsection{Hydrodynamics and Gravity}
\label{sec:hydro}

We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}). Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc). At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation. \citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse. \textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.

\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas. These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution. At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr. We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$. These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions. This threshold decreases the required run-time by factors of a few. The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}

\subsection{Chemistry and Cooling Physics}
\label{sec:chemistry}

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code. We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.

>>>>

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\shorttitle{Differential Metal Mixing}

@@

%\title{Evolution of Individual Metals in Galactic Winds and the ISM}

% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
\title{Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{{\it more...}}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds. Only 80\% of metals dominated by AGB enrichment are ejected through winds, even though 95\% of all metals leave the galaxy. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

\keywords{}

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (review refs for obs and theory). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x. stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas. (\textit{... more...})
% Discuss common modeling assumptions in CE models that
%    can be addressed here:
%        1) instantaneous recycling approximation
%        2) No metal mass loading of winds, or uniform 
%           loading across species
%        3) Uniform metal abundances across the ISM (one zone)
%
%  To some degree, cosmological simulations with comparably
%     low spatial resolution face the same problems, where
%     variations and spreads in abundances (esp. across 
%     species) can be smoothed over due to the low res. or
%     the particular details of the feedback methods and
%     yield injection methods.

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (references), which plays an important role in determining the chemical properties of galaxies (references). % more on mixing
Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. (\textit{... more...}) That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

% Paragraphs
It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group. (APOGEE, GAIA, GALAH, RAVE? TGAS?). Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.

% Can shorten if this is actually going to be a letter
In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy. The simulation discussed here was first introduced in detail in Emerick et. al. 2018 (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. [list examples of modelling problems]. These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study. By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here. This work will be the first in several in attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.

We summarize of our methods and physics models in Section~\ref{sec:methods}. We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}. In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.

\section{Methods}
\label{sec:methods}
We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.

\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}. Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver. We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc. Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells. If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution. At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.

\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}. We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely. Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}. Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.

\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$. Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$). We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%. Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment. We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).

\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind. Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.

\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}. We initialize a M$_{\rm gas} = 1.8 \times 10^{6} M_{\odot}$ disk with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$ using an exponential gas profile. The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc. Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium. The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy. Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero. Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.

\section{Results}
For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy. \textbf{UPDATE VALS:  In general, this galaxy has an average star formation rate of $4~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.  The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy. The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$. These winds eject 90\% of the metals produced in the galaxy, with 40\% of all metals leaving the virial radius by the end of the simulation time. }

In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy. We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.

%\begin{figure}
%\centering
%\includegraphics[width=0.95\linewidth]{sfr_snrx100_agb.png}\\
%\caption{}
%\label{fig:sfr}
%\end{figure}

\subsection{Preferential Ejection of Metals from the ISM}
\label{sec:ejection}

\begin{figure}
\centering
\includegraphics[width=0.99\linewidth]{species_bar.png}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals. \textbf{Need to font sizes and mass labels}}
\label{fig:species_fractions}
% GB(AE): Why are H and He different? Either discuss or remove from plot.
%  ------ AE removed from plot
%
\end{figure}

The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow). Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
